Deep Learning

### 2015-02-17 deepreview.tex
typos

Deep Learning techniques allow a machine composed of multiple layers
of processing to learn to represent data, so that each layer transform
the representation of the previous layer in a more abstract
fashion. These methods have dramatically improved the state-of-the-art
for speech recognition, object recognition, object detection,
predicting the activity of drug molecules, and many other tasks. Deep
learning discovers intricate structure in large datasets by using the
{\em backpropagation algorithm} to compute how the machine should
change in order to make less errors.  Deep {\em convolutional nets}
have brought about dramatic improvements in the processing of array
data, such as images, video, speech and audio, while {\em recurrent
  net} have shown excellent performance for analyzing sequential
inputs and producing sequential outputs such as text and
speech. Convolutional net has quickly become the leading for image
recognition and speech recognition, while recurrent nets are
competitive in several natural language processing tasks, including
language translation. Combinations of recurrent and convolutional nets
can generate good textual captions of images.

@@

% handcrafted features
Traditional ML techniques are limited in their ability to process
natural data in raw form. For decades, constructing a pattern
recogntion or ML system has required engineering efforts and domain
expertise to design a {\em feature extractor} that transforms the raw
data, such as the pixel values of an image, into a suitable {\em
  internal representation}, or feature vector, from which the learning
subsystem, often a classifier, can detect, recognize, or classify
patterns in the input.

% deep learning: learning representations
Deep learning is a set of methods that allows a machine to be fed with
raw data and to automatically discover suitable representations of the
data. The name comes from the fact that deep learning machines are
multilayer stacks of trainable modules, each of which turns the
representation of the data in its input into a more abstract and
higher-level representation on its output in which relevant
characteristics and amplified and irrelevant variabilities are
attenuated. For example, an image comes in the form of an array of
pixel values, features in the first layer would represent the presence
or absence of edges of a particular orientation at all locations in
the image, the second layer would detect motifs by spotting particular
arrangements of edges, regardless of small variations in the positions
of the edges.  The third layer would assemble motifs into parts of
object, and subsequent layers would detect objects as combinations of
parts. The key aspect of deep learning is that {\em these features and
  representations are not designed by human engineers, but are
  automatically learned from data.}

>>>>

Deep Learning techniques allow a machine composed of multiple layers
of processing to learn to represent data, so that each layer transforms
the representation of the previous layer in a more abstract
fashion. These methods have dramatically improved the state-of-the-art
for speech recognition, object recognition, object detection,
predicting the activity of drug molecules, and many other tasks. Deep
learning discovers intricate structure in large datasets by using the
{\em backpropagation algorithm} to compute how the machine should
change in order to make less errors.  Deep {\em convolutional nets}
have brought about dramatic improvements in the processing of array
data, such as images, video, speech and audio, while {\em recurrent
  nets} have shown excellent performance for analyzing sequential
inputs and producing sequential outputs such as text and
speech. Convolutional nets have quickly become the leading technology for image
recognition and speech recognition, while recurrent nets are
competitive in several natural language processing tasks, including
language translation. Combinations of recurrent and convolutional nets
can generate good textual captions of images.

@@

% handcrafted features
Traditional ML techniques are limited in their ability to process
natural data in raw form. For decades, constructing a pattern
recognition or ML system has required engineering efforts and domain
expertise to design a {\em feature extractor} that transforms the raw
data, such as the pixel values of an image, into a suitable {\em
  internal representation}, or feature vector, from which the learning
subsystem, often a classifier, can detect, recognize, or classify
patterns in the input.

% deep learning: learning representations
Deep learning is a set of methods that allows a machine to be fed with
raw data and to automatically discover suitable representations of the
data. The name comes from the fact that deep learning machines are
multilayer stacks of trainable modules, each of which turns the
representation of the data in its input into a more abstract and
higher-level representation on its output in which relevant
characteristics and amplified and irrelevant variabilities are
attenuated. For example, an image comes in the form of an array of
pixel values, features in the first layer would represent the presence
or absence of edges of a particular orientation at all locations in
the image, the second layer would  detect motifs by spotting particular
arrangements of edges, regardless of small variations in the positions
of the edges.  The third layer would assemble motifs into parts of
object, and subsequent layers would to detect objects as combinations of
parts. The key aspect of deep learning is that {\em these features and
  representations are not designed by human engineers, but are
  automatically learned from data.}
